---
title: "Belief in Free Will"
subtitle: " A Catalyst for Long-Term Job Satisfaction in the Workplace"
author: 
  - Hailey Jang
  - Joe Zhou
thanks: "Code and data are available at: https://github.com/Hailey-Jang/STA302_Reproduction.git"
date: 02-13-2024
date-format: long
abstract: "This paper investigates the long-term relationship between belief in personal freedom and job satisfaction through two longitudinal studies. Study 1 tracked 252 Taiwanese real-estate agents over 3 months, while Study 2 followed 137 American workers in an online labour market over 6 months. We found a consistent positive correlation between belief in free will and job satisfaction, even after accounting for other agency constructs. This research highlights the enduring impact of embracing personal freedom on workplace contentment, offering valuable insights for enhancing individual well-being and organizational productivity in diverse cultural and occupational settings."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```

# Introduction

In today's dynamic and demanding work environments, the pursuit of job satisfaction is a fundamental aspect of individual well-being and organizational productivity. Central to this pursuit is the belief in personal freedom, an age-old philosophical concept that has garnered renewed attention for its potential practical implications. Extensive research has already established a significant correlation between the belief in free will and work performance, suggesting that this philosophical stance might offer tangible psychological benefits. However, while existing studies provide valuable insights, they often lack long-term investigation into the enduring relationship between belief in free will and job satisfaction. Addressing this gap, our research endeavors to explore the longitudinal association between these factors, shedding light on their lasting impact on individuals' satisfaction with their work.

In our quest to delve deeper into this intriguing connection, we conducted two distinct yet complementary studies. Study 1 involved a cohort of 252 Taiwanese real-estate agents, meticulously tracked over a period of three months. Through comprehensive assessments, we examined the correlation between the participants' belief in free will and their reported levels of job satisfaction. Study 2 broadened the scope by focusing on 137 American workers engaged in an online labor market, monitored diligently over six months. Leveraging similar methodologies, we sought to corroborate and extend the findings from Study 1, thereby providing a robust understanding of the relationship between belief in free will and job satisfaction across diverse cultural and occupational contexts.

Our findings unveil a compelling narrative: a consistent and positive relationship exists between the belief in free will and job satisfaction over extended periods of time. Both studies revealed that individuals who embrace the notion of personal freedom tend to experience higher levels of satisfaction in their professional endeavors. Remarkably, this association persisted even when accounting for other agency constructs, underscoring the unique and enduring impact of belief in free will on workplace contentment.

Understanding the profound influence of belief in free will on job satisfaction holds profound implications for both individuals and organizations alike. By elucidating this enduring relationship, our research not only enriches scholarly discourse but also offers actionable insights for enhancing workplace well-being and productivity. This paper unfolds in three sections: first, we provide a comprehensive review of the literature on belief in free will and its implications for job satisfaction. Next, we detail the methodologies employed in our two longitudinal studies, followed by a presentation and analysis of our findings. Finally, we offer a nuanced discussion of the theoretical implications, practical applications, and avenues for future research in this burgeoning field.

# Data 

# Study 1
The dataset comprises responses gathered from surveys conducted within 54 branch offices of a publicly listed real-estate agency company in Taiwan. Two waves of surveys, separated by a 3-month time-lag, were administered to agents, resulting in a total of 293 returned questionnaires at Time 1 and 252 at Time 2, with a 74% response rate. The dataset encompasses several variables shedding light on agents' demographics, free will perception, and job satisfaction levels. Key variables include age (E_AGE), sex (E_SEX), free will perception, job satisfaction at Time 1 (JS), and job satisfaction at Time 2 (W2JS). Notably, age exhibits a mean of approximately 30.5 years at both time points, with a slight increase in the mean age at Time 2. Regarding sex distribution, the majority of respondents identify as male, comprising approximately 79-82% of the sample across both time points. 

## Study 1-a set-up
```{r}
library(ggplot2)
library(dplyr)
library(tidyr)
```

```{r}
data <- read.csv("FW satisfaction-Study 1-data.csv")

data <- na.omit(data)

str(data)
```

```{r}
ggplot(data, aes(x = freewill, y = JS)) +
  geom_point(color = "blue") +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  labs(title = "Relationship between Free Will Belief and Job Satisfaction",
       x = "Belief in Free Will",
       y = "Job Satisfaction (Time 1)") +
  theme_minimal()
```
```{r}
ggplot(data, aes(x = freewill, y = W2JS)) +
  geom_point(color = "blue") +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  labs(title = "Relationship between Free Will Belief and Job Satisfaction",
       x = "Belief in Free Will",
       y = "Job Satisfaction (Time 2)") +
  theme_minimal()
```
### Model Justification
In examining the scatter plots representing job satisfaction levels over Time 1 and Time 2, as well as the relationship between belief in free will and changes in job satisfaction over time, a notable trend emerges. The scatter plots depict a discernible upward trend, indicating that individuals with stronger convictions in free will tend to exhibit higher levels of job satisfaction. This observation is particularly evident in the second scatter plot, where the change in job satisfaction over time is plotted against the belief in free will. Here, the trendline illustrates a clear positive slope, suggesting that as belief in free will increases, so does job satisfaction.

## Study 1-b set-up
```{r}
ggplot(data, aes(x = JS)) +
  geom_histogram(fill = "skyblue", color = "black", bins = 20) +
  labs(title = "Distribution of Job Satisfaction at Time 1",
       x = "Job Satisfaction",
       y = "Frequency") +
  theme_minimal()

ggplot(data, aes(x = W2JS)) +
  geom_histogram(fill = "lightgreen", color = "black", bins = 20) +
  labs(title = "Distribution of Job Satisfaction at Time 2",
       x = "Job Satisfaction",
       y = "Frequency") +
  theme_minimal()
```
### Model Justification
A comparison between job satisfaction at Time 1 and Time 2 shows a slight increase in satisfaction levels during Time 2, albeit not statistically significant. The distribution plot depicting job satisfaction at both time points illustrates a positive trend, with most data points shifting upwards from Time 1 to Time 2, indicating a general improvement in satisfaction over the 3-month period. This observation is further supported by the histograms, where the distribution of job satisfaction scores at Time 2 appears to be slightly shifted towards higher values compared to Time 1. While the difference may be subtle, it suggests a trend of increasing job satisfaction among agents over time within the surveyed branch offices. Additional statistical analysis could provide further insights into the significance and drivers of this observed change.


# Model 2
## Model set-up
### Model Justification

# Discussion 
## discussion point


# References
